Table

### 2025-09-16 manuscript/terms_table.qmd
child qmd

---
title: "Table"
format: pdf
bibliography: bibliography.bib

---

```{r setup}
#| include: false
library(knitr)
library(tidyverse)
library(flextable)
library(ftExtra)

@@

@@

  rename(Term = X, "Definition and deliberation" = Y)

flextable(terms, cwidth = c(1, 5)) |>
  ftExtra::colformat_md() |>
  valign(j = 1, valign = "top", part = "all")
```

>>>>

```{r setup2}
#| include: false
library(knitr)
library(tidyverse)
library(flextable)
library(ftExtra)

@@

#| tbl-cap: "Key terms and concepts as they are used in this paper."

@@

  rename("Term or concept" = X, "Definition and deliberation" = Y)

flextable(terms) |>
  width(j = 1, width = 1) |>     # Relative width
  width(j = 2, width = 5) |>     # Relative width  
  valign(j = 1:2, valign = "top", part = "all") |>
  ftExtra::colformat_md(j = 2)
